Shallow EDSLs and Object-Oriented Programming

### 2016-06-24 paper/sections/ShallowOO.tex
Clean up Haskell code

This section shows that an OO approach and shallow embeddings using
procedural abstraction are closely related.  We use a subset of the
DSL presented in Gibbons and Wu's paper~\cite{gibbons2014folding} as
the running example.  We first give the original shallow embedded
implementation in Haskell and gradually rewrite it towards an ``OO
style''.  Then translating the program into an OO language becomes
straightforward.

@@

\paragraph{Towards OOP}
A simple, \emph{semantics preserving}, rewriting of the above program 
uses a record implemented as a newtype. The record has a sole field representing the result:
\lstinputlisting[linerange=30-35]{./code/shallowCircuit.hs}%APPLY:CIRCUIT3
%\bruno{width3 should now be width2}
%We no longer need a separate \lstinline{width3} function as the field name is the extractor.
The implementation is still shallow since essentially the same program
as the previous one. In fact Haskell \lstinline{newtype} do not add any operational
behaviour to the program, and the two programs are effectivelly the
same.  However, having fields makes the program look more like an 
OOP program.

>>>>

This section shows that an OO approach and shallow embeddings using
procedural abstraction are closely related.  We use a subset of the
DSL presented in Gibbons and Wu's paper~\cite{gibbons2014folding} as
the running example.  We first give the original shallow embedded
implementation in Haskell and rewrite it towards an ``OO style''.
Then translating the program into an OO language becomes straightforward.

@@

\paragraph{Towards OOP}
A simple, \emph{semantics preserving}, rewriting of the above program 
uses a record implemented as a newtype. The record has a sole field representing the result:
\lstinputlisting[linerange=2-5]{./code/Rewrite.hs}%APPLY:CIRCUIT3
%\bruno{width3 should now be width2}
%We no longer need a separate \lstinline{width3} function as the field name is the extractor.
The implementation is still shallow because \lstinline{newtype} does not add any operational
behaviour to the program, and hence the two programs are effectivelly the
same.  However, having fields makes the program look more like an 
OOP program.

### 2016-06-24 paper/sections/Transformations.tex
Clean up Haskell code

\section{Transformations in Shallow Embeddings}
Transformations are typically regarded as the privilege of deep embeddings as no
persistent AST obscures how to define transformations in shallow embeddings.
The \textsc{Composite} pattern applied in our OO approach encodes the AST, making
it possible to implement transformations. More interestingly, we can port back
some simple transformations to Haskell.
This sections illustrates how to define transformations, the missing kind of interpretations in Gibbons and Wu's paper, in shallow embeddings.

@@

%\weixin{define a show function in the and show the result after desugaring?}
We can port the implementation back to Haskell thanks to its laziness:
\lstinputlisting[linerange=6-21]{./code/desugar.hs}%APPLY:DESUGAR

>>>>

\section{Transformations in Shallow Embeddings}
Transformations are typically regarded as the privilege of deep embeddings as no
persistent AST obscures how to define transformations in shallow embeddings.
The \textsc{Composite} pattern applied in our OO approach encodes the AST, making
it possible to implement transformations. More interestingly, we can port back
some simple transformations to Haskell.
This section illustrates how to define transformations, the missing kind of interpretations in Gibbons and Wu's paper, in shallow embeddings.

@@

%\weixin{define a show function in the and show the result after desugaring?}
We can port the implementation back to Haskell thanks to its laziness:
\lstinputlisting[linerange=6-21]{./code/Desugar.hs}%APPLY:DESUGAR
